Predicting Bike Usage at UofT St. George Campus with Bayesian Poisson Regression

### 2024-12-14 paper/paper.qmd
title adjusted
title adjusted

---
title: "Predicting Bike Usage at UofT St. George with Bayesian Poisson Regression"
subtitle: "Daily usage grows by one every 20 days, drops to between 0 and 3 in winter, with 79% occurring between 8 AM and 8 PM"
author: 
  - Haowei Fan
thanks: "Code and data are available at: https://github.com/HaoweiFan0912/Bikeshare-Forecast.git"
date: today
date-format: long
abstract: "University of Toronto's St. George campus students and staff frequently encounter challenges in locating available bike-sharing parking spots upon arrival and bikes upon leaving [@elassi2017bike], underscoring the necessity for accurate predictions of future bike-sharing demand to optimize campus commuting infrastructure. This study employs Bayesian Poisson regression to predict the utilization of bike-sharing stations at 27 locations across campus for specific years, months, and four-hour intervals of the day. The results show that daily bike-sharing usage on campus increases by one every 20 days but decreases to between 0 and 3 in winter months, and 79% of peak usage consistently observed between 8:00 AM and 8:00 PM daily. Specifically, on September 26, 2025, between 4:00 and 8:00 AM, the usage of 8 stations is projected to increase by 3 bikes, 14 stations by 2 bikes, 3 stations by 1 bike, while 1 station will remain unchanged, and 1 station will see a decrease by 1 bike, compared to the same timeframe in 2024."
format: pdf
toc-depth: 2    
number-sections: true
toc: true           
toc-title: "Table of Contents" 
bibliography: references.bib
---

>>>>

---
title: "Predicting Bike Usage at UofT St. George Campus with Bayesian Poisson Regression"
subtitle: "Daily usage grows by one every 20 days, drops to between 0 and 3 in winter, with 79% occurring between 8 AM and 8 PM"
author: 
  - Haowei Fan
thanks: "Code and data are available at: https://github.com/HaoweiFan0912/Bikeshare-Forecast.git"
date: today
date-format: long
abstract: "University of Toronto's St. George campus students and staff frequently encounter challenges in locating available bike-sharing parking spots upon arrival and bikes upon leaving [@elassi2017bike], underscoring the necessity for accurate predictions of future bike-sharing demand to optimize campus commuting infrastructure. This study employs Bayesian Poisson regression to predict the utilization of bike-sharing stations at 27 locations across campus for specific years, months, and four-hour intervals of the day. The results show that daily bike-sharing usage on campus increases by one every 20 days but decreases to between 0 and 3 in winter months, and 79% of peak usage consistently observed between 8:00 AM and 8:00 PM daily. Specifically, on September 26, 2025, between 4:00 and 8:00 AM, the usage of 8 stations is projected to increase by 3 bikes, 14 stations by 2 bikes, 3 stations by 1 bike, while 1 station will remain unchanged, and 1 station will see a decrease by 1 bike, compared to the same timeframe in 2024."
format: pdf
toc-depth: 2    
number-sections: true
toc: true           
toc-title: "Table of Contents" 
bibliography: references.bib
---
